### 2009-07-09 docs/architecture/architecture.tex
more stubs

@@

\begin{figure}[t]
\centering
\includegraphics[width=6.5in]{\archfigpath/data_loc2}
\caption{\label{fig:dataloc} Some of the different data-centerings: (a) cell-centered, (b) nodal in the $x$-direction, and (c) nodal in both the $x$- and $y$-directions.}
\end{figure}

@@

@@

\section{MAESTRO Modules}

@@

>>>>

On a grid, the data can be stored at cell-centers, on a face/edge, or
on the corners.  In boxlib, data that is on an edge is termed `nodal'
in that direction (see figure~\ref{fig:dataloc}.  Data that is on the
corners is nodal in all spatial directions.  In MAESTRO, the state
data (density, enthalpy, velocity, $\ldots$) is generally
cell-centered.  Fluxes are nodal in the direction they represent.
A few quantities are nodal in all directions (e.g.\ $\phi$ used in
the final velocity projection).

\begin{figure}[h]
\centering
\includegraphics[width=6.5in]{\archfigpath/data_loc2}
\caption{\label{fig:dataloc} Some of the different data-centerings:
  (a) cell-centered, (b) nodal in the $x$-direction, and (c) nodal in
  both the $x$- and $y$-directions.  Note that for nodal data, the
  integer index corresponds to the lower boundary in that direction.
  In each of these centerings, the red point has the same indices:\ (1,2).
  Not show is the case where data is nodal in the $y$-direction only.}
\end{figure}

@@

@@

\section{MAESTRO Data Organization}

The state of the star in MAESTRO is described by both a
multidimensional state and the 1D base state.  The full
multidimensional state is stored in \multifab s while the base state
is simply stored in Fortran arrays.

\subsection{`{\tt s}' and `{\tt u}' \multifab s}

\subsection{\tt umac}

\subsection{Base State Arrays}

\subsection{Other Quantities}

@@

\section{MAESTRO Helper Modules}

@@

The {\tt variables} module provides
